\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-06-28 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratios $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary numbers $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width

>>>>

Viscous finger morphologies were investigated by \citet{guan_2003} based on mathematical formulation and semi-analytic solutions of the coupled Darcy and continuity equations developed by \citet{mclean_1981}. A sensitivity study was conducted to assess the impact on fingers' formation, dimensions and branchiness for a range of viscosity ratio $\left(\right.$10$^{2}\le\textit{VR}\le$10$\left.^{4}\right)$ and modified capillary number $\left(\right.$632$\le N_{C}^{'}\le$6.32$\times$10$^{7}$, with $N_{C}^{'}= U\mu\gamma^{-1}(W/b)^{2}$, where $U$ is the velocity of the finger, $W$ is half Hele-Shaw cell width and $b$ is the cell thickness$\left.\right)$. Finger width $\left(\lambda_{f}\right)$ and volumetric flow rate $\left(\mathcal{Q}\right)$ at the outflow region are correlated through \citep{guan_2003}, 
\begin{equation} 
   \mathcal{Q} = U b \lambda_{f}.\label{eqn:guaneqn} 
\end{equation} 
Numerical simulation performed with {\it VR} of 10 and 150 showed finger width of approximately 0.45-0.70 and \blue{XX (Jeff)} cm (Fig.\blue{XX}), respectively, which are close match to the expected from equation

### 2017-06-28 Papers/ViscousInstabilities/article_figure1.tex
updates

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c}}
\vspace{0.cm}
\hbox{\hspace{3.5cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c}
      \includegraphics[width=.6\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{4.5cm} (e)t=10.00s}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves. The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage

@@

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-1cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
      \hbox{\hspace{2.0cm} (a) t=0\red{??} \hspace{5.cm} (b) t=500\red{(???)} \hspace{4.0cm} (c) t=2000\red{(???)}}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
      \hbox{\hspace{1.0cm} (d) t=3000\red{??} \hspace{5.cm} (e) t=6000\red{(???)} \hspace{3.0cm} (f) t=24000\red{(???)}}}
\caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$. The domain contains \red{XXXX} elements.}
\label{fig:HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.9\textwidth, height=0.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D201c}
\hspace{0.5cm}      
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D1001c}}
\vspace{0.cm}
\hbox{\hspace{5.cm} (a) t=0.66s \hspace{8.cm} (b) t=3.43s }
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2001c}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201c}
      \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D3001c}}
\vspace{0.cm}
\hbox{ \hspace{2.cm} (c) t=6.92s \hspace{4.5cm} (d) t=7.61s \hspace{4.5cm} (e)t=10.00s}
\vspace{0.cm}
}   
\caption{Simulated flow in a Hele-Shaw cell ({\it VR}=10): snapshots of overlapped wetting phase saturation and velocity vectors showing flow profile as the simulation evolves. The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10}
\end{figure}
\end{landscape}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[ht] 
 \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}
       \includegraphics[width=.5\textwidth]{./Pics1/Saffman_homogeneous_VR10/ST_Homog_VR10_D2201_bbd}}
\caption{Simulated flow in a Hele-Shaw cell for viscosity ratio of 10 (left) and 150 (right \red{to be added}). \blue{ Jeff: Add comments here wrt to  tip width as a model validation wrt Saffmann's and  Guan's papers.} The domain contains $26313$ \PN[1]{2} triangular elements.}
\label{fig:homoheleshaw_VN10_VN250}
\end{figure}

@@

%%%
%%% FIGURE XXXXXX
%%%
\begin{landscape}
  \begin{figure}[ht]
  \vbox{\vspace{-1cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_1.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_500.pdf} 
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_2000.pdf} }
      \hbox{\hspace{1.0cm} (a) map of permeabilities \hspace{3.cm} (b) t=0.75s \hspace{4.0cm} (c) t=8s}
      \vspace{0.5cm}
      \hbox{\includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_3000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_6000.pdf}
            \includegraphics[width=.5\textwidth]{./Pics1/Saffman_heterogeneous/saffman_heter_fixed_24000.pdf} }
      \hbox{\hspace{2.5cm} (d) t=18s \hspace{5.cm} (e) t= \hspace{3.0cm} (f) t=24000 }}
\caption{Simulated flow in a modified Hele-Shaw cell with (a) prescribed distribution of permeability field $\left(\text{10}^{-10}\le\mathbf{K}_{1}\le\text{5}\times\text{10}^{-10}\right.$. The domain contains \red{XXXX} elements.}
\label{fig:HeleShawHeter_VR10}
\end{figure}
\end{landscape}
\clearpage
